---
title: "EIA API wrapper for R"
output: 
  md_document:
    variant: markdown_github
---

# Introduction

An R client for the EIA API. The API is currently in beta and can be subject to
change.

Before you do anything head over to the [EIA registration page](http://www.eia.gov/beta/api/register.cfm)
and get an API key.

# Installation

```
devtools::install_github("krose/eia")

```

# Examples

```{r, echo=FALSE}
source("api_key.R")
```

Let's first load the library:

```{r loadeia, echo=TRUE}

library(eia)

```

## Category

The first function is the category function. If you don't supply any category_id you will simply
data on the top level category returned as a list:

```{r cat1, echo=TRUE}

eia_cat(api_key = api_key)

```

These categories are deep, so you might find yourself searching through these until you get
to the data series that you are interested.

Here's the first level natural gas category:

```{r cat2, echo=TRUE}

eia_cat(api_key = api_key, category_id = "714804")

```

When you get to the final level the result is often a long list of "childseries" which id's the data
series you can request.

```{r cat3, echo=TRUE}
eia_cat(api_key = api_key, category_id = 475136)
```

## Series

Let's take a look at the annual series from North Dakota and Montana where a part of the Bakken formation is.

```{r series1, echo=TRUE}

eia_series(api_key = api_key,
           series_id = c("NG.RES_EPG0_R5302_SND_BCF.A", "NG.RES_EPG0_R5302_SMT_BCF.A"))

```

That's a lot of information and I would rather have it in a more tidy format. When you select "tidy_long"
two additional columns are added descriping the series time frame and the series_id.


```{r series2, echo=TRUE}

eia_series(api_key = api_key, 
           series_id = c("NG.RES_EPG0_R5302_SND_BCF.A", "NG.RES_EPG0_R5302_SMT_BCF.A"),
           tidy_data = "tidy_long", 
           only_data = TRUE)

```


